---
title: "Example exercises 1A"
subtitle: "intro2r flipped workshop"
author: "John Little"
date: "`r Sys.Date()`"
output: html_notebook
---

**dplyr**

These exercises supplement the first part of the [flipped workshop _Introduction to R_](https://rfun.library.duke.edu/).  The workshop is in two parts

- Part 1: getting started, EDA, data wrangling
- Part 2: visualization, pivot, join, regression

The [YouTube playlist of all the videos](https://www.youtube.com/playlist?list=PLIUcX1JrVUNWBUl4Cwu8psxxDVZCvrJHk) is publicly available under a CC-BY license

Beyond the exercises included in this repository, the workshop code base is here:  https://github.com/libjohn/rfun_flipped 

## Load library packages

```{r}
install.packages("gapminder")
library(tidyverse)
library(gapminder)
```

## Data

The data are [an excerpt from the Gapminder dataset](https://github.com/jennybc/gapminder)

```{r}
glimpse(gapminder)
```


## subset data

- select
- filter
- arrange

### select

Subset the tibble (data frame) by columns.  Display only the year and the population columns

```{r}
gapminder %>% 
  select(year, pop)
```

### filter

Gather population data for the year 1987

```{r}
gapminder %>% 
  filter(year == 1987)
```

### arrange

1. sort by populations
2. sort continent in reverse alphabetical order

    a. subsort in reverse chronological by year

```{r}
gapminder %>% 
  arrange(pop)

gapminder %>% 
  arrange(desc(continent), desc(year))
```

## Manipulate data

- mutate
- count 
- summarize
- group_by

### mutate

Create a new variables.  Multiply `lifeExp` by 2.

```{r}
gapminder %>% 
  mutate(life_dbl = round(lifeExp * 2))
```

### count

How many observations exist for each country within the data set.

```{r}
gapminder %>% 
  count(country)
```

#### distinct

Sometimes you just want to know the values within a variable...

List the distinct values within the continent column

```{r}
gapminder %>% 
  distinct(continent)
```

### summarize

Calculate the total of a single column.  In this case sum all the values in the `pop` column.

```{r}
gapminder %>% 
  summarize(sum_of_pop = sum(pop))
```

Of course, it makes no sense to total that column but now you know how to get column totals.  Generally we summarize subtotals using `group_by` along with summarize.

```{r}
gapminder %>% 
  group_by(year) %>% 
  summarise(total_pop_by_year = scales::comma(sum(pop)))
```

Calculate the total and the mean population by year, per continent

```{r}
gapminder %>% 
  group_by(year, continent) %>% 
  summarise(total_pop_by_year = scales::comma(sum(pop)), mean(pop))
```

