---
title: "Example exercises 1B"
subtitle: "intro2r flipped workshop"
author: "John Little"
date: "`r Sys.Date()`"
output: html_notebook
---

**very quick visualization and EDA**

These exercises supplement the first part of the [flipped workshop _Introduction to R_](https://rfun.library.duke.edu/).  The workshop is in two parts

- Part 1: getting started, EDA, data wrangling
- Part 2: visualization, pivot, join, regression

The [YouTube playlist of all the videos](https://www.youtube.com/playlist?list=PLIUcX1JrVUNWBUl4Cwu8psxxDVZCvrJHk) is publicly available under a CC-BY license

Beyond the exercises included in this repository, the workshop code base is here:  https://github.com/libjohn/rfun_flipped 

## Load library packages

```{r}
library(tidyverse)
library(gapminder)
library(skimr)
```

## Data

The data are from the dplyr::starwars dataset consisting of information about _Star Wars_ characters

```{r}
glimpse(starwars)
```

## Scatterplot

```
ggplot(data = some_tibble, aes(x =, y =)) +
  geom_somefunction()
```

Make a scatter plot from the `starwars` tibble using `ggplot2::geom_point()`.  Use `height` as the predictor variable and `mass` as the response variable.  Limit the results to characters with a mass less than 500 Kg.

```{r}

```

###  EDA

Use the `skimr` library package to `skim` the gapminder tibble

```{r}

```



