---
title: "02 Vizualization - part A"
author: "John Little"
date: "`r Sys.Date()`"
#output: html_notebook
---

## Load library Packages

```{r}
library(tidyverse)
# library(gapminder)
```


## data

These exercisees use the following [`ggplot2` training datasets](https://ggplot2.tidyverse.org/reference/index.html#section-data)

- ggplot2::mpg
- ggplot2::midwest
- ggplot2::economics_long


## Scatter plot

Starting with the `mpg` dataset, 

a. Make a scatterplot using displacement (`displ`) as the predictor value on the x axis and highway mpg (`hwy`) as the response variable.
b. Color each variable by the type of car (`class`)
c. Add a regression line for each type of car


```{r}
mpg %>% 
  ggplot(aes(___, ___)) +
  geom_point(aes(color = ___)) + 
  geom_-----(aes(group = ___)) 
```



```{r}
mpg %>% 
  ggplot(aes(displ, hwy)) +
  geom_point(aes(color = class)) +
  geom_smooth(aes(group = class, color = class),  se = FALSE, method = lm)
```

## Bar plots

a. Using the `ggplot::midwest` dataset, display a barplot of each category showing the categorical frequency
b. Arrange the bars in order from most frequent to least
c. Make the plot a stacked bar chart, stacked by state

### geom_bar()

```{r}
midwest %>% 
  ggplot() +
  geom_bar(aes(____))
```


```{r}
midwest %>% 
  ggplot() +
  geom_bar(aes(fct_-------(_______), fill = ______)) 
```

### geom_col()

With the `geom_col` function, the height of the bars represent values in the data

a. Make a bar plot showing the total population in each state.  One way to do this is to use `dplyr` functions learned in part 1 of the _flipped_ series
b. Arrange the bars in descending order of frequency.  Using one of the `scales_` functions, affect the scale to be a more human readable label with commas

```{r}
midwest %>% 
  group_by(______) %>% 
  summarise(state_pop = sum(_______)) %>% 
  ggplot(aes(_____, _____)) +
  geom_col()
```


```{r}
midwest %>% 
  group_by(state) %>%
  summarise(state_pop = sum(poptotal)) %>% 
  ggplot(aes(fct_rev(fct_reorder(state, state_pop)), state_pop)) +
  geom_col() +
  scale_y_continuous(labels = scales::comma)
```
## geom_line

Using the `ggplot2::economics_long` dataset

a.  Draw a time-series line plot of the various values in the tibble.  Use the `group` argument 
b.  Improve the plot by adding colors to each line.
c.  Eliminate the `pop` variable and show the remaining four variables in a faceted view with `facet_wrap()`

```{r}
economics_long %>% 
  ggplot(aes(_____, _____)) +
  geom_line(aes(color = _____))
```


```{r}
economics_long %>% 
  filter(variable != "pop") %>% 
  ggplot(aes(date, value)) + 
  geom_line(aes(color = variable)) +
  facet_wrap(~ _______)
```

## Interactive Plots

```{r}
library(plotly)
```

```{r}
interactive_barplot <- midwest %>% 
  ggplot() +
  geom_bar(aes(fct_infreq(category), fill = state)) 

interactive_barplot

ggplotly(interactive_barplot)
```

