---
title: "02 pivot and join - part B"
author: "John Little"
date: "`r Sys.Date()`"
#output: html_notebook
---

```{r}
library(tidyverse)
```

## data

These exercisees use the following [`ggplot2` training datasets](https://ggplot2.tidyverse.org/reference/index.html#section-data)

-   dplyr::starwars
-   Data from fivethrityeight.org
-   ggplot2::economics
-   ggplot2::economics_long

## Join

There are a series of [join commands](https://dplyr.tidyverse.org/reference/index.html#section-two-table-verbs)

-   left_join, inner_join, right_join, full_join,
-   semi_join, anti_join

First let's read in the favorability ratings data from fivethirtyeight.com

```{r}
fav_ratings <- read_csv("data/538_favorability_popularity.csv", skip = 11)
fav_ratings
```

Join on a key that is common across two data frames. For best results use a numeric key that promotes precision. Of course, we're going to use a alphabetic key, `name`, which will highlight what can go wrong and introduce troubleshooting strategies.

Anyway, in this case, the key will be the `name` variable that is common to both tables. We're using the `fav_ratings` tibble and the `starwars` tibble.

```{r}
fav_ratings %>% 
  # left_join(starwars, by = c("name" = "name"))
  left_join(starwars)  %>% 
  arrange(desc(fav_rating))
```

```{r}
anti_join(fav_ratings, starwars) %>% arrange(name)
anti_join(starwars, fav_ratings) %>% arrange(name)
```

```{r}
starwars %>% 
  filter(str_detect(name, regex("3p|palpatine|obi|amidala|leia|d2", ignore_case = TRUE))) %>% 
  arrange(name)
```

## Pivot

```{r}
economics
economics_long %>% arrange(date)
```

```{r}
economics %>% 
  pivot_longer(pce:unemploy, names_to = "variable", values_to = "value") 
```


